Improved Cation Binding to Lipid Bilayer with Negatively Charged POPS by Effective Inclusion of Electronic Polarization

### 2019-10-31 Manuscript/manuscript.tex
Update text

\includegraphics[height=1.4 in]{../img/TOC_graphic.pdf}

For table of contents only.

@@

Recent analyzes of interaction sites between calcium and PS lipids combining
MD simulations with various experimental techniques remain controversial 
as the results strongly depend on force fields parameters \cite{melcrova16,valentine18,hallock18, NMRlipidsIV}.
Here, we analyze the calcium binding details of POPC:POPS (5:1) mixture with 409 mM CaCl$_2$ from ECC-lipids simulations,
which surpass the quality of other force fields in direct comparison with experimental order parameters.
In the ECC-lipid simulation, calcium ions binds approximately twice more likely 
to the carboxylate than to the phosphate moiety of POPS headgroup,
while binding only to acyl chain carbonyls is almost negligible (Fig.~\ref{fig:cacl_complexes} and Table~\ref{tab:binding}).
The result is consistent with CHARMM36 simulations without the NBfix correction \cite{hallock18},
but CHARMM36 simulations with the NBfix correction \cite{kim16} predict almost exclusive binding to carboxylate group \cite{valentine18}
and Berger simulations show signifincant binding affinity also to acyl chain carbonyls \cite{melcrova16}.
On the other hand, calcium ions bind too strongly on bilayers simulated using CHARMM36 without the NBfix correction
or Berger models, and too weakly on CHARMM36 bilayers with the NBfix correction \cite{catte16,NMRlipidsIV}.
Furthermore, in CHARMM36 simulations without the NBfix,
calcium ions coordinate with even four distinct PS lipids \cite{hallock18}, while coordination with more than two PS lipids
is very rare in our ECC-lipids simulations (Fig.~\ref{fig:cacl_complexes}).

@@

The following files are available free of charge. 
\begin{itemize} 
  \item SI.pdf: Additional simulation and experimental details, figures and tables. 
\end{itemize}

>>>>

\includegraphics[height=1.375 in]{../img/TOC_graphic.pdf}

@@

Recent analyzes of interaction sites between calcium and PS lipids combining
MD simulations with various experimental techniques have been controversial 
because the results strongly depend on force fields parameters \cite{melcrova16,valentine18,hallock18, NMRlipidsIV}.
Here, we analyze the calcium binding details of POPC:POPS (5:1) mixture with 409 mM CaCl$_2$ from ECC-lipids simulations,
which surpass the quality of other force fields in direct comparison with experimental order parameters.
In the ECC-lipid simulation, calcium ions binds approximately twice more likely 
to the carboxylate than to the phosphate moiety of POPS headgroup,
while binding only to acyl chain carbonyls is almost negligible (Fig.~\ref{fig:cacl_complexes} and Table~\ref{tab:binding}).
The result is consistent with CHARMM36 simulations without the NBfix correction \cite{hallock18},
but CHARMM36 simulations with the NBfix correction \cite{kim16} predict almost exclusive binding to carboxylate group \cite{valentine18}
and Berger simulations show signifincant binding affinity also to acyl chain carbonyls \cite{melcrova16}.
On the other hand, calcium ions bind too strongly on bilayers simulated using CHARMM36 without the NBfix correction
or Berger models, and too weakly on CHARMM36 bilayers with the NBfix correction \cite{catte16,NMRlipidsIV}.
Furthermore, in CHARMM36 simulations without the NBfix,
calcium ions coordinate with even four distinct PS lipids \cite{hallock18}, while coordination with more than two PS lipids
is very rare in our ECC-lipids simulations (Fig.~\ref{fig:cacl_complexes}).

@@

The following files are available free of charge. 
\begin{itemize} 
\item SI.pdf: Measured 1D and 2D NMR spectra, additional details and results from simulations
  about monovalent ion binding, configurations and populations of bound calcium to POPS lipids, and
  residence times of bound calcium.
\end{itemize}
